---
output: html_document
---
Elements Of Data Visualization: Project 1
===
__By Alex Cortez, Adam Hernandex, and Alex Pearce__

__GitHub__: https://github.com/alexpearce92/DV_RProject1.git

In this project, the group familiarizes itself with git, knitr, ggplot, and basic SQL commands to create **interesting** plots of given data. Additionally, we create graphs usings the entire data set via a provided SQL query. 

## We will first create our data frames.

####We load the necessary libraries ...
```{r message=F, warning=F}
library('RCurl')
library('ggplot2')
```

####Then we query the database to generate our data frames
```{r}
orders.df <- data.frame(eval(parse(text=substring(getURL(URLencode('http://129.152.144.84:5001/rest/native/?query="select * from orders"'), httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDB1.usuniversi01134.oraclecloud.internal', USER='DV_ORDERS', PASS='orcl', MODE='native_mode', MODEL='model', returnFor = 'R', returnDimensions = 'False'), verbose = TRUE), 1, 2^31-1))))

customers.df <- data.frame(eval(parse(text=substring(getURL(URLencode('http://129.152.144.84:5001/rest/native/?query="select * from customers"'), httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDB1.usuniversi01134.oraclecloud.internal', USER='DV_ORDERS', PASS='orcl', MODE='native_mode', MODEL='model', returnFor = 'R', returnDimensions = 'False'), verbose = TRUE), 1, 2^31-1))))

order_details.df <- data.frame(eval(parse(text=substring(getURL(URLencode('http://129.152.144.84:5001/rest/native/?query="select * from order_details"'), httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDB1.usuniversi01134.oraclecloud.internal', USER='DV_ORDERS', PASS='orcl', MODE='native_mode', MODEL='model', returnFor = 'R', returnDimensions = 'False'), verbose = TRUE), 1, 2^31-1))))

items.df <- data.frame(eval(parse(text=substring(getURL(URLencode('http://129.152.144.84:5001/rest/native/?query="select * from items"'), httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDB1.usuniversi01134.oraclecloud.internal', USER='DV_ORDERS', PASS='orcl', MODE='native_mode', MODEL='model', returnFor = 'R', returnDimensions = 'False'), verbose = TRUE), 1, 2^31-1))))
```

####Here are the dataframes we just created
```{r}
customers.df
items.df
order_details.df
orders.df
```

##Now we create "interesting" graphs:

####Here we can see that most customers hail from California. How delightfully intriguing. 

```{r}
ggplot(data = customers.df) + geom_histogram(aes(x = CUSTOMER_STATE))
```

####And here, It appears some artist price their worth more than others but, no higher than 17 and no less than 13 price units. Quite a fascinating aspect of the data. 

```{r}
ggplot(items.df, aes(x = ARTIST, y = UNIT_PRICE)) + geom_point()
```

####Here we see that some item ID's have more individual orders (not accounting for quantity of order), than others. Item ID 1 seems to be the hottest commodity! 

```{r}
ggplot(data = order_details.df, aes(x = ITEM_ID)) + geom_histogram(binwidth = 1, aes(fill = ..count..))
```

####Finally we take a look at the number of orders per month. This was done by some initial data subsetting, followed by a ggplot function. It appears this company does poorly during September and October. Unfortunate. 

```{r}
months <- as.vector(substr(orders.df$ORDER_DATE,6,7))
months <- data.frame(months)
ggplot(data = months) + geom_histogram(aes(x = months ))
```


##Now to recreate some other interesting graphs using several joins in the creation of our dataframe:

####We first query the database with our SQL statement
```{r}
set.df <- data.frame(eval(parse(text=substring(getURL(URLencode('http://129.152.144.84:5001/rest/native/?query="select * from orders o join customers c on o.customer_id = c.customer_id join order_details d on o.order_id = d.order_id join items i on d.item_id = i.item_id"'), httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDB1.usuniversi01134.oraclecloud.internal', USER='DV_ORDERS', PASS='orcl', MODE='native_mode', MODEL='model', returnFor = 'R', returnDimensions = 'False'), verbose = TRUE), 1, 2^31-1))))
```

####Now let's build some graphs
```{r message=F, warning=F}
ggplot(set.df, aes(x = as.Date(ORDER_DATE, "%Y-%m-%d"), y = as.Date(SHIPPED_DATE,"%Y-%m-%d"))) + geom_point(aes(color = as.factor(UNIT_PRICE))) + facet_wrap(~CUSTOMER_STATE)

ggplot(set.df, aes(x = as.Date(ORDER_DATE, "%Y-%m-%d"), y = as.Date(SHIPPED_DATE,"%Y-%m-%d"))) + geom_point(aes(color = as.factor(TITLE))) + facet_wrap(~CUSTOMER_STATE)

ggplot(set.df, aes(x = as.Date(ORDER_DATE, "%Y-%m-%d"), y = as.Date(SHIPPED_DATE,"%Y-%m-%d"))) + geom_point(aes(color = as.factor(ARTIST))) + facet_wrap(~CUSTOMER_STATE)
```