---
output: html_document
---
Elements Of Data Visualization: Project 1
===
__By Alex Cortez, Adam Hernandex, and Alex Pearce__

__GitHub__: https://github.com/alexpearce92/DV_RProject1.git

In this project, the group familiarizes itself with git, knitr, ggplot, and basic SQL commands to create **_interesting_** plots of given data. Additionally, we create graphs usings the entire data set via a provided SQL query. 

## We will first create our data frames.

####We load the necessary libraries ...


```{r message=F}
library('RCurl')
library('ggplot2')
```

####Then we query the database to generate our data frames
```{r}
source("../01 Data/create_data_frames.R", echo = TRUE)
```

####Here are the dataframes we just created
```{r}
head(customers.df)
head(items.df)
head(order_details.df)
head(orders.df)
```

##Now we create "interesting" graphs:

####Below, we can see that most customers hail from California. How delightfully intriguing. 

```{r fig.width=12, fig.height=7.5}
source("../02 Visualizations/generate_plot_customers.R", echo = TRUE)
```

####Now we look at the unit price an artist charges for an album. It appears that artists priced their albums at $17 with a much higher frequency than they priced their albums at $13. _Interesting_.

```{r fig.width=12, fig.height=7.5}
source("../02 Visualizations/generate_plot_items.R", echo = TRUE)
```

####Here we see which item has been asked for the most by customers. Item ID 1 seems to be the hottest commodity! 

```{r fig.width=12, fig.height=7.5}
source("../02 Visualizations/generate_plot_order_details.R", echo = TRUE)
```

####Finally, we take a look at the number of orders per month. This was done by some initial data manipulation. It appears this company does poorly during September and October. Unfortunate.
We first subsetted the code to extract the months, generated a table of the frequency of occurance for each month, then applied ggplot() to our new data frame.

```{r fig.width=12, fig.height=7.5}
source("../02 Visualizations/generate_plot_order_date.R", echo = TRUE)
```


##Now to recreate some other interesting graphs using several joins in the creation of our dataframe:

####We first query the database with our SQL statement
```{r}
source("../01 Data/create_data_frame_joined.R", echo = TRUE)
```

####Now let's build some graphs
```{r fig.width=12, fig.height=7.5}
source("../02 Visualizations/recreate_plot_1.R", echo = TRUE)
source("../02 Visualizations/recreate_plot_2.R", echo = TRUE)
source("../02 Visualizations/recreate_plot_3.R", echo = TRUE)
```